Classless Java

### 2016-03-24 OOPSLA16/sections/Introduction.tex
Improved intro in classlessJava

A key challenge in IB lies in how to model state, which is
fundamental to have stateful objects. All abstract operations in an
object interface are interpreted as \emph{abstract state
  operations}. The abstract state operations include various common
utility methods (such as getters and setters, or clone-like
methods). Objects are only responsible to define the ultimate
behaviour of a method and, for example, if such a method is just a
setter. Anything related to state is completely contained in the
instances and does not leak into the inheritance logic.  In CB, the structure of the state is fixed and can be only grown
by inheritance.  In contrast, in IB the state is never
fixed, and methods that look like abstract setters and getters
can always receive an explicit implementation down in the inheritance
chain, improving \textbf{modularity and flexibility}.  That is, the
concept of abstract state is more fluid.

@@

\item {\bf Classless Java:} a practical realization of IB in
  Java. Classless Java is implemented using annotation processing, 
  allowing most tools to work transparently with our approach. 
  We provide examples, informal and formal descriptions of Classless
  Java.

>>>>

A key challenge in IB lies in how to model state, which is
fundamental to have stateful objects. All abstract operations in an
object interface are interpreted as \emph{abstract state
  operations}. The abstract state operations include various common
utility methods (such as getters and setters, or clone-like
methods). Objects are the only responsible to define the ultimate
behaviour of a method and, for example, if such a method is just a
setter. Anything related to state is completely contained in the
instances and does not leak into the inheritance logic.  In CB, the structure of the state is fixed and can be only grown
by inheritance.  In contrast, in IB the state is never
fixed, and methods that look like abstract setters and getters
can always receive an explicit implementation down in the inheritance
chain, improving \textbf{modularity and flexibility}.  That is, the
concept of abstract state is more fluid.

@@

\item {\bf Classless Java:} a practical realization of IB in
  Java. Classless Java is implemented using annotation processing, 
  allowing most tools to work transparently with our approach. 
  We provide examples, informal and formal descriptions of Classless
  Java.
  Existing Java projects can use our approach and still be
  backward compatible with their client, in a way that is formally specified
  by our safety properties.
